\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{OpenTable - Scenarios}
\author{Leo Sicard}
%\date{}               % Activate to display a given date or no date

\begin{document}
\maketitle

\section{The Coffee Shop}

Alice is supposed to meet her friend Bob in a Coffee Shop.
She arrives early, and chooses to sit at one of the interactive tables.
After ordering a drink via the digital interface, she takes her phone out of her purse and places it on the table.
A dialog pops up next to her smartphone.
Alice confirms the UI transfer by a simple touch, and her phone's interface appears as a mirrored display on the table, seemingly attached to her physical device.
She resizes the window to her convenience, and moves it closer to her by sliding her phone on the surface.
Alice accesses her own applications on the larger surface while waiting for Bob.
She types and sends an email, updates her facebook profile, and browses the internet.

When Bob arrives, Alice minimizes her display, keeping her phone in place.
Bob orders a drink and start telling about his recent holiday.
He places his own smartphone on the table, thus establishing a UI transfer, in order to show Alice a few pictures.
When done, Bob disconnects his phone by simply lifting it off the table.
They had planned to go to a photography exhibition.
Alice restores her phone's display on the table and opens a browser in order to check the museum's location and opening hours.

\section{The Meeting}

Jim, Jack and Jill are having a meeting about the development of a software product.
They are sitting around an interactive table, with different artefacts, including paper, pens, computing devices and coffee cups.
Jill is responsible for the meeting's agenda, which is stored on her smartphone.
She has placed her phone on the table, established a UI transfer, and opened the said document.
The display occupies only a portion of the table, but is conveniently placed so as to allow Jim and Jack visual reference to the different discussion points.

It is now time for Jack to present a diagram of the development process.
He switches on his tablet computer, opens said diagram, and places the tablet on the table for the others to see.
The screen is however too small, so Jack decides instead to use the UI transfer application.
By a simple touch, Jack attaches the UI to the table, allowing him to remove the physical tablet while keeping the mirrored display active.
With the help of gestures, he resizes and rotates the window, and presents the diagram to his colleagues.
The diagram stays on the table during the whole meeting.
However, when Jack is about to leave, he switches off his tablet computer, which has the effect of interrupting the connection to the tabletop, thus keeping the diagram private.

\section{The Office}

It is monday morning and Bill arrives at his office.
His desk is an interactive table.
On it are a laptop computer, stacks of papers, books, pens, an empty cup and a lamp.
Bill powers up the tabletop and laptop, and places his smartphone on the table.
Bill's smartphone is known to the tabletop, and therefore a UI transfer is automatically established in dual view mode, allowing Bill to drag widgets out of his smartphone.
Bill places its calender up in one corner, together with its Skype widget.
After reading through his mail on the laptop computer, Bill starts typing an answer, for which he needs to refer to a document that is stored on his phone.
Bill switches the UI tranfer to a mirror mode, causing the phone's display to appear on the desk alongside the device.
By sliding the phone, he moves the display to a convenient location.
Suddenly the phone rings.
Bill attaches all applications and UI display to the table, allowing him to pick up the phone without interrupting the UI transfer.


\end{document}  