\chapter{Design - scenarios}
\label{scenarios}

\subsubsection*{The coffee shop: single user with a public tabletop}

Alice is sitting in a Coffee Shop, waiting for her friend Bob.
The table is an interactive surface, which allows her to order a drink via the digital interface.

She takes her phone and notebook out of her purse and places them on the table. 
A dialog pops up on her smartphone, asking her if she wants to establish the connection between the two devices.
Alice confirms this by a simple tap.
A menu appears on the table beside her phone. 
Alice taps the `Connect' button, and her phone's display appears on the table beside her phone.

She resizes the window to her convenience, and moves it closer by sliding her phone on the surface. 
Alice accesses her phone's applications, and starts typing an email.

When Bob arrives, Alice minimizes the surface application, keeping her phone in place. 
Bob orders a drink and they start catching up. 
After a while, Bob leaves. 
Alice restores the application, finishes up her email, and exits the application by lifting the phone off the table.

\subsubsection*{The meeting: multiple users with a public tabletop}

Jim, Jack and Jill are having a meeting about the development of a product. 
They are sitting around an interactive table with different artifacts, including paper, pens, computing devices and coffee cups. 
Jill is responsible for the meeting's agenda, which is stored on her smartphone.

Jill places her phone on the top right corner of the table and establishes a UI transfer. 
She uses the `Grab' button to drag the display window to the left of the phone where there is space. 
She opens the document containing the agenda, and uses the `Resize' corner of the window to enlarge the display, in order to allow all to see.

Now it is time for Jack to present a diagram of the development process. 
He switches on his tablet computer, opens said diagram, and places the tablet on the table for the others to see. 
However the screen is too small, so instead Jack decides to use the UI transfer application. 
With a single tap on the `Grab' button, Jack pins the UI to the table, allowing him to remove the physical tablet while keeping the transferred display active. 
By using the `Resize' corner, he enlarges and flips the orientation of the window to a landscape view. 
By the use of a double touch on the `Grab' tab and the active window, Jack rotates the display to a convenient position, and presents the diagram to his colleagues. 
When finished, Jack minimizes the window by tapping a button. 
The window takes the shape of an active icon, ready to be restored or closed as convenient. 
When the meeting is over, Jack taps the `Close' tab on the icon to exit the application.

\subsubsection*{The office: single user with a private tabletop}

It is monday morning and Bill arrives at his office. 
His working desk is an interactive table extended with a vertical screen, a mouse and a keyboard. 
On it are various physical objects, including a stack of papers, some books, pens, an empty cup and a lamp.

Bill wakes the tabletop up from its standby state by simply placing his smartphone on it. 
The devices know each other, so a UI transfer is automatically launched. 
Bill uses a widget on his phone to push application widgets to the table space. 
Bill places his calendar up in one corner, together with his Skype widget.

After reading through his mail on the vertical screen, Bill starts typing an answer using the keyboard. 
He needs to refer to a document that is stored on his phone. 
Bill uses the `Grab' button beside his phone to attach the display beside the device. 
He enlarges the window and moves the display to a convenient location by sliding the phone. 
Bill types on.

Suddenly the phone rings. 
Bill taps the `Grab' button to effectively pin all applications and UI display to the tabletop, allowing him to pick up the phone without interrupting the UI transfer.
